---
title: 'Homework 3'
author: "Ryan"
date: "2/10/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Due: 2/17/2022 before 11:59pm. Submit in Canvas (file upload).

## Git
Ryan Repository: https://github.com/ryancorydon8/practice1-ryancorydon8
Emma Repository: https://github.com/epodlich/practice1-epodlich

I made 4 pull requests on Emma's repository after I forked her repository and made changes under mine.There was a at least 18 commits.

Emma made 3 pull requests on my repository and merged successfully. There was at least 14 commits.



## Question 2: 3 Tips to make git hub easier

First I would say how to understand a forked repository and make a pull request into the main repository. The most important thing is practice with git because after multiple attempts it becomes a lot easier to understand. As well understand R and pushing the files from R into git. This takes practice and to understand it best it is important to make sure you clone the repository and connect it via version control in R.

## Question 3

Generate the graph of LifExp vs. gdpPercap for US, Canada (fixed data) and Australia by RMarkdown based on the data set "gapminder-5060", like what we did in the class.  
Please use Github to collaborate on this problem. For example, one member can create the plot of US in his/her repository. The other member will fork this repository, add the result for the second country, and make a pull request for merging into the main repository. Each member should at least analyze one country and make at least one pull request. **Please submit the RMarkdown file, the output file, and the screen shot of the successful pull request and the merge.**


# Add the United States - Ryan

```{r}
library(ggplot2)
life5060 <- read.csv("https://raw.githubusercontent.com/epodlich/practice1-ryancorydon8/main/gapminder-5060%20.csv")
View(life5060)
dim(life5060)
us <- life5060[life5060$country == "United States", ]
head(us)
dim(us)
ggplot(data = us, aes(x = year, y = lifeExp)) + geom_line()
```

```{r}
us_fixed = us
us_fixed$lifeExp[us_fixed$year==1957] = 69.49
us_fixed
ggplot(data = us_fixed, aes(x = year, y = lifeExp)) + geom_line()
```


# Add Canada - Emma

# Unfixed Data Plot

```{r}
life5060 <- read.csv("https://raw.githubusercontent.com/epodlich/practice1-ryancorydon8/main/gapminder-5060%20.csv")
View(life5060)
dim(life5060)
canada <- life5060[life5060$country == "Canada", ]

head(canada)
dim(canada)
ggplot(data = canada, aes(x = year, y = lifeExp)) + geom_line()
```
# Fixed Data Plot

```{r}
canada_fixed = canada
canada_fixed$lifeExp[canada_fixed$year==1957] = 69.96
canada_fixed
ggplot(data = canada_fixed, aes(x = year, y = lifeExp)) + geom_line()
```

## Question Four

Write a paragraph (~200 words) describing an example of what you consider data science. Write your paragraph in R Markdown. Include at least 
    a. one link to a chart or an image and 
    b. at least one itemized or enumerated list.
    
Data science is the extraction of knowledge from complex data through several different techniques like machine learning. A great example that I will discuss and am extremely interested in is sports data and analytics. You can use this to find numerous different types of data to help a team or a player. For example if a coach has data on a player he can make informed decisions that can effect game strategy or selection when it comes to using a certain player at a certain time based on the data. AS well, fan behavior can be generated when organizations produce special events to see if more fans arrive, as well if players play better at said special events. I like looking at prime time stats compared to regular time stats because it is interesting to see how different players play on the big stage. Data science and technology has changed the way sports have been played and it is only making the game more advanced than ever imagined. 
This is an example of how Kirk Cousins plays during specific times and the odds of them performing better or worse.  https://ftw.usatoday.com/wp-content/uploads/sites/90/2022/09/Screen-Shot-2022-09-20-at-10.35.55-AM.png


## This is how I rank my interest in different sports I would consider working in after I graduate.
1. Soccer
2. Football
3. Baseball
4. Golf
5. Hockey
5. Basketball
  


